Exploring the conformational dynamics of alanine dipeptide in solution subjected to an external electric field: A nonequilibrium molecular dynamics simulation

### 2014-02-24 writedown/npt-neq/alanine.tex
revise

In the present paper, we study a small peptide, alanine dipeptide, as a model for showing how the method can be used. 
The choice of a small peptide, rather than a larger one, is done firstly because it
is easier to draw clear conclusions on the nonequilibrium properties
of a single peptide by excluding the slow-going interplay between
different peptide segments along a chain. 
Secondly, the computational cost required is rather massive and thus  testing
the various methodology proposed here would be hampered for large molecules,
although they remain our goal.  In any case, alanine dipeptide
is large enough so that the conformational changes of its internal degrees of freedom represent valid observables for a test of validity and utility of our approach.
The paper is organized as follows:
  We firstly describe the idea of D-NEMD, and propose a technical improvement consisting in the definition and application of a local thermostating process.
Next, after introducing the physical
observables chosen to analyze the nonequilibrium response,
the numerical results for the case of a static and oscillatory EF, respectively, are discussed. By calculating the nonequilibrium properties from D-NEMD
simulations, we are able to address
a few relevant questions: (i)~How the conformation of the peptide
changes in an EF (conformational space);
(ii)~When these changes happen (time scale),
and how likely they are (probability). 
To our knowledge, this study is one of the few (if not the first)  where
time-dependent nonequilibrium w.r.t. conformation
is explicitly considered for a (relatively large) molecule
in solution subject to an external time-dependent EF.

@@

The time-dependent probability density of the system to stay in a certain
conformation is given in
Fig.~\ref{fig:tmp5}.
\recheck{The simulation results of starting one branching trajectory
  from each initial conformation are compared with those starting
  four branching trajectories from each initial conformation (each with
  different random seed for the Langevin thermostat).
  They are consistent within the statistical uncertainty, which
  means our simulation result is robust with respect to the randomness
  introduced by the (local) Langevin thermostat.
}
The $\beta$-sheet conformations $\confba$ and $\confbb$,
which are present at the initial stage after EF is switched on,
\recheck{fade away as the system relaxes}. The
probability of the $\alpha$-helix conformation $\confaa$, grows from 0.45 to 0.69.
The $\alpha$-helix $\confab$  does not change significantly  under the action of EF.
The left-hand helix conformation $\confc$ noticeably grows from 0 to 0.22.
We plot the net probability fluxes in Fig.~\ref{fig:tmp6}.
Results show that for short $t$, the net fluxes are generally non-zero,
however, 
as $t$ goes to infinity,
all fluxes converge to zero. This indicates
that as the EF is switched on, the system first is driven away from the initial
equilibrium (at zero EF);  This is a nonequilibrium process.
\recheck{After a time long enough, the system
is fully relaxed to the new conformations,
and stays there as long as the EF is kept. However, whether the new conformations
are in the new equilibrium defined the constant EF is not clear, because
there may exist very slow nonequilibrium processes, for example as long as 1~$\mu$s,
which cannot be discovered by our nonequilibrium simulation of only 1~ns.
What we can do by the proposed nonequilibrium simulation
method is to study time-dependent behaviours that are no longer than
the simulation time. 
}
% After a time long enough, the system
% is fully relaxed to the new equilibrium defined by the action of the constant EF,
% and stays there as long as the EF is kept.
An important point is that despite the system is finally relaxed to the new conformation,
the relaxation timescales corresponding to each conformation are rather different. 
From Fig.~\ref{fig:tmp5} and \ref{fig:tmp6}, we observe mainly
three different timescales 10~ps, 100~ps and 500~ps,
whose corresponding conformations are summarized in Tab.~\ref{tab:tmp1}.
This is a relevant result because it shows the possibility of employing an external EF as a tool to identify relevant time scales in the conformational behaviour of a molecule in solution.

@@

Fig.~\ref{fig:tmp9} shows the probability of the
conformations against time for periodically oscillatory EF,
while  
Fig.~\ref{fig:tmp10} presents the integrated net probability fluxes
(defined by Eqn.~\eqref{eqn:tmp7a}) between
conformations. Here the probability fluxes are not reported
because the profiles are highly oscillating and they would not offer 
a better information than the one that can be obtained from the integrated probability flux.
Coming back to Fig.~\ref{fig:tmp9}, for all periods investigated,
the observed time-dependent probabilities  in $\confaa$, $\confab$, $\confba$ and $\confbb$ are
highly oscillating and the average value over time cycles does not change
considerably w.r.t.~time.
However, the probability in conformation $\confc$ significantly
increases to approximately 0.17 for $\period =10$~ps, 0.27 for  $\period =40$~ps, and
0.26 for $\period =200$~ps.
In the case of $\period =10$ and $40$~ps, {the probability of conformation $\confc$}
reaches the steady value in around 300~ps, while it requires about 1200~ps
for the $\period =200$~ps case. 
The notable increment of probability of $\confaa$ and
  the vanishing of $\confba$ in the constant EF case (see Fig.~\ref{fig:tmp5})
are not observed in the oscillatory EF case.
\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{fig.ala.new/graphs/graph-t0010-2.eps}
  \caption{Schematic plot of the main probability flux between conformations
    for periodically oscillatory EF, $\period =10$~ps. The thickness 
    of the arrows approximately presents the strength of the flux.
    The numbers near the arrows indicates the strength of the averaged
    probability flux, the unit of which is $10^{-3}\times\textrm{ps}^{-1}$.
  }
  \label{fig:tmp11}
\end{figure}
In comparison to the static EF case, where the probability flux
vanishes when the system reaches steady state (Fig.~\ref{fig:tmp6}), 
Fig.~\ref{fig:tmp10} shows increasing
integrated probability net fluxes, which imply some lasting and directional
fluxes among the conformations (see Fig.~\ref{fig:tmp9}).
Fig.~\ref{fig:tmp11} presents
a schematic plot of the main probability fluxes for $\period =10$~ps.
The thickness of the arrows and the numbers nearby indicate
the steady value of average net fluxes over periods.
The relevance of Fig.~\ref{fig:tmp11} is in the fact that it suggests,
in perspective, a general scenario common to all molecules
characterized by $\beta$-sheet-like or $\alpha$-helix-like
conformations and how an electric field is likely to modify it.
\recheck{
  Although the conformational transitions presented Fig.~\ref{fig:tmp11} are studied under
  the nonequilibrium scenario, it is actually qualitatively similar to those
  discovered in the equilibrium studies, e.g.~\cite{apostolakis1999calculation, gfeller2007complex}.
}
The probability flux of $\period =40$~ps is quantitatively
comparable to the case $\period =10$~ps, except that the probability fluxes
going into conformation $\confc$ is stronger, which actually results in
a higher steady probability in $\confc$.
The probability flux of case $\period =200$~ps is qualitatively
similar to $\period =10$~ps and $\period =40$~ps, however,
the strength is much lower than the latter two cases.
Moreover, 
  we see that the integrated fluxes reach
  a steadily
increasing stage after about 3200~ps, which is even longer than the time scale
at which the probability of $\confc$ reaches its steady value. This indicates
a longer intrinsic time scale in the $\period =200$~ps case.

@@

>>>>

In the present paper, we study a small peptide, alanine dipeptide, as a model for showing how the method can be used. 
The choice of a small peptide, rather than a larger one, is done firstly because it
is easier to draw clear conclusions on the nonequilibrium properties
of a single peptide by excluding the slow-going interplay between
different peptide segments along a chain. 
Secondly, the computational cost required is rather massive and thus  testing
the various methodology proposed here would be hampered for large molecules,
although they remain our goal.  In any case, alanine dipeptide
is large enough so that the conformational changes of its internal degrees of freedom represent valid observables for a test of validity and utility of our approach.
The paper is organized as follows:
  We firstly describe the idea of D-NEMD, and propose a technical improvement consisting in the definition and application of a local thermostating process.
Next, after introducing the physical
observables chosen to analyze the nonequilibrium response,
the numerical results for the case of a static and oscillatory EF, respectively, are discussed. By calculating the nonequilibrium properties from D-NEMD
simulations, we are able to address
a few relevant questions: (i)~How the conformation of the peptide
changes in an EF (conformational space);
(ii)~When these changes happen (time scale),
and how likely they are (probability).
\recheck{
  In the appendix of the paper, we also compare our nonequilibrium method with
  the equilibrium linear response theory,
  which is able to study the nonequilibrium properties
  by only calculating equilibrium correlation functions.}
To our knowledge, this study is one of the few (if not the first)  where
time-dependent nonequilibrium w.r.t. conformation
is explicitly considered for a (relatively large) molecule
in solution subject to an external time-dependent EF.

@@

The time-dependent probability density of the system to stay in a certain
conformation is given in
Fig.~\ref{fig:tmp5}.
\recheck{The simulation results of starting one branching trajectory
  from each initial conformation are compared with those starting
  four branching trajectories from each initial conformation (each with
  different random seed for the Langevin thermostat in the thermostated region).
  They are consistent within the statistical uncertainty, which
  means our simulation result is robust with respect to the randomness
  introduced by the (local) Langevin thermostat.
}
The $\beta$-sheet conformations $\confba$ and $\confbb$,
which are present at the initial stage after EF is switched on,
\recheck{fade away as the system relaxes}. The
probability of the $\alpha$-helix conformation $\confaa$, grows from 0.45 to 0.69.
The $\alpha$-helix $\confab$  does not change significantly  under the action of EF.
The left-hand helix conformation $\confc$ noticeably grows from 0 to 0.22.
We plot the net probability fluxes in Fig.~\ref{fig:tmp6}.
Results show that for short $t$, the net fluxes are generally non-zero,
however, 
as $t$ goes to infinity,
all fluxes converge to zero. This indicates
that as the EF is switched on, the system first is driven away from the initial
equilibrium (at zero EF);  This is a nonequilibrium process.
\recheck{After a time long enough, the system
is fully relaxed to the new conformations,
and stays there as long as the EF is kept. However, whether the new conformations
are in the new equilibrium defined the constant EF is not clear, because
there may exist very slow nonequilibrium processes, for example as long as 1~$\mu$s,
which cannot be discovered by our nonequilibrium simulation of only 1~ns.
What we can do by the proposed nonequilibrium simulation
method is to study time-dependent behaviours that are no longer than
the simulation time. 
}
% After a time long enough, the system
% is fully relaxed to the new equilibrium defined by the action of the constant EF,
% and stays there as long as the EF is kept.
An important point is that despite the system is finally relaxed to the new conformation,
the relaxation timescales corresponding to each conformation are rather different. 
From Fig.~\ref{fig:tmp5} and \ref{fig:tmp6}, we observe mainly
three different timescales 10~ps, 100~ps and 500~ps,
whose corresponding conformations are summarized in Tab.~\ref{tab:tmp1}.
This is a relevant result because it shows the possibility of employing an external EF as a tool to identify relevant time scales in the conformational behaviour of a molecule in solution.

@@

Fig.~\ref{fig:tmp9} shows the probability of the
conformations against time for periodically oscillatory EF,
while  
Fig.~\ref{fig:tmp10} presents the integrated net probability fluxes
(defined by Eqn.~\eqref{eqn:tmp7a}) between
conformations. Here the probability fluxes are not reported
because the profiles are highly oscillating and they would not offer 
a better information than the one that can be obtained from the integrated probability flux.
Coming back to Fig.~\ref{fig:tmp9}, for all periods investigated,
the observed time-dependent probabilities  in $\confaa$, $\confab$, $\confba$ and $\confbb$ are
highly oscillating and the average value over time cycles does not change
considerably w.r.t.~time.
However, the probability in conformation $\confc$ significantly
increases to approximately 0.17 for $\period =10$~ps, 0.27 for  $\period =40$~ps, and
0.26 for $\period =200$~ps.
In the case of $\period =10$ and $40$~ps, {the probability of conformation $\confc$}
reaches the steady value in around 300~ps, while it requires about 1200~ps
for the $\period =200$~ps case. 
The notable increment of probability of $\confaa$ and
  the vanishing of $\confba$ in the constant EF case (see Fig.~\ref{fig:tmp5})
are not observed in the oscillatory EF case.
\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{fig.ala.new/graphs/graph-t0010-2.eps}
  \caption{Schematic plot of the main probability flux between conformations
    for periodically oscillatory EF, $\period =10$~ps. The thickness 
    of the arrows approximately presents the strength of the flux.
    The numbers near the arrows indicates the strength of the averaged
    probability flux, the unit of which is $10^{-3}\times\textrm{ps}^{-1}$.
  }
  \label{fig:tmp11}
\end{figure}
In comparison to the static EF case, where the probability flux
vanishes when the system reaches steady state (Fig.~\ref{fig:tmp6}), 
Fig.~\ref{fig:tmp10} shows increasing
integrated probability net fluxes, which imply some lasting and directional
fluxes among the conformations (see Fig.~\ref{fig:tmp9}).
Fig.~\ref{fig:tmp11} presents
a schematic plot of the main probability fluxes for $\period =10$~ps.
The thickness of the arrows and the numbers nearby indicate
the steady value of average net fluxes over periods.
The relevance of Fig.~\ref{fig:tmp11} is in the fact that it suggests,
in perspective, a general scenario common to all molecules
characterized by $\beta$-sheet-like or $\alpha$-helix-like
conformations and how an electric field is likely to modify it.
\recheck{
  Although the network presented Fig.~\ref{fig:tmp11} is similar to those
  discovered in the equilibrium studies, e.g.~\cite{apostolakis1999calculation, gfeller2007complex}
  in the sense of the steady conformations and connections among them,
  the physical meaning is quit different in our study:
  The system is under the nonequilibrium condition, and
  the fluxes are lasting. In contrast,
  such probability fluxes do not exist in the equilibrium case.
  % Although the conformational transitions presented Fig.~\ref{fig:tmp11} are studied under
  % the nonequilibrium scenario, it is actually qualitatively similar to those
  % discovered in the equilibrium studies, e.g.~\cite{apostolakis1999calculation, gfeller2007complex}.
}
The probability flux of $\period =40$~ps is quantitatively
comparable to the case $\period =10$~ps, except that the probability fluxes
going into conformation $\confc$ is stronger, which actually results in
a higher steady probability in $\confc$.
The probability flux of case $\period =200$~ps is qualitatively
similar to $\period =10$~ps and $\period =40$~ps, however,
the strength is much lower than the latter two cases.
Moreover, 
  we see that the integrated fluxes reach
  a steadily
increasing stage after about 3200~ps, which is even longer than the time scale
at which the probability of $\confc$ reaches its steady value. This indicates
a longer intrinsic time scale in the $\period =200$~ps case.

@@

  \appendix
\section{Comparison with the linear response theory}  
\recheck{
A commenly used equilibrium method that is able to study the nonequilibrium
responses is the linear responses thoery (Green-Kubo relation~\cite{green1954markoff,kubo1957statistical}).
We also use it to test the
conformational dynamics of alanine dipeptide under the EF.
The response function, take the time-dependent probability of
left-handed $\alpha$-helix for example, is defined as~\cite{tuckeman2010statistical}
\begin{align}\label{eqn:appdx1}
  P_\confc(t) = \langle\chi_{\confc}(t)\rangle = \langle \chi_{\confc} \rangle_0 -
  \beta \int_0^t ds\; M_e(t - s)\langle j(0)\cdot \chi_{\confc}(t) \rangle_0,
\end{align}
where $\chi_{\confc}$ is the characteristic function of set $\confc$ that takes
the value of 1 for $(\phi,\psi)\in \confc$, and takes value 0
otherwise. $M_e(t)$ is the relative magnitude of the EF. Take the case of
constant EF for example, $M_e(t) = t/t_{warm}$ for $0\leq t<t_{warm}$, and
$M_e(t) = 1$ for $t\geq t_{warm}$.
$j$ is the dissipative flux that is defined by
\begin{align}
  j = - \sum_{i=1}^N E_\infty q_i v_{i,x},
\end{align}
where $q_i$ is the partial charge of the $i$th atom, and $v_{i,x}$ is
the $x$ component of the velocity of the $i$th atom.  The notation
$\langle\cdot\rangle_0$ denotes the equilibrium ensemble average.
We plot the correlation function
$\langle j(0)\cdot \chi_{\confc}(t) \rangle_0$ against corrlation time $t$
in Fig.~\ref{fig:appdx1}. The value of the function is estimated from
two independent 1~$\mu$s equilibrium simulations.
Please notice that the total length of the equilibrium
trajactories is the same as the nonequilibrium simulation (2000
trajactories, each 1000~ps long).
% With the knowledge of
% nonequilibrium simulation, the correlation function is expected to
% vanish at roughly 500~ps, however, it does not vanish even at
% 1000~ps. This is not surprising, because
We find that the statistical error is even larger than the value of
corrlation function.  Therefore, the
overwhelming statistical uncertainty does not allow us to use it 
in Eq.~\eqref{eqn:tmp1} to calculate the
nonequilibrium averages. 
% , and we actually do not know when the
% corrlation function vanish .
Since the total computational effort of
the equilibrium simulation is the same as the nonequilibrium
simulation, we conclude that nonequilibrium simulatoin is more
precise than the conventional equilibrium approach (linear response) at the same computational cost.
A similar
observation has already been reported by Ciccotti and Jacucci~\cite{ciccotti1975direct}.
}

\begin{figure}
  \centering
  \includegraphics{fig.ala.new/fig-corr-meta.eps}
  \caption{The corrlation function $\langle j(0)\cdot \chi_{\confc}(t)
    \rangle_0$ against time $t$. The error bars in the figure denote
    the statistical uncertainty at 95\% confidence level. }
  \label{fig:appdx1}
\end{figure}

### 2014-02-24 writedown/npt-neq/reply/reply.tex
revise

Another commenly used equilibrium method that is able to study the non-equilibrium
responses is the linear responses thoery (Green-Kubo relation).
We also use it to test the
conformational shift of alanine dipeptide under the electric field
(EF). The response function, take the time-dependent probability of
left-handed $\alpha$-helix (Conformation $C$ in the old manuscript. The notation has been changed to $\alpha_L$ in the updated manuscript.) for example, is defined as
\begin{align}\label{eqn:tmp1}
  P_C(t) = \langle\chi_{_C}(t)\rangle = \langle \chi_{_C} \rangle_0 -
  \beta \int_0^t ds\; M_e(t - s)\langle j(0)\cdot \chi_{_C}(t) \rangle_0
\end{align}
where $\chi_{_C}$ is the characteristic function of set $C$ that takes
the value of 1 for $(\phi,\psi)\in C$, and takes value 0
otherwise. $M_e(t)$ is the magnitude of the EF. In the case of
constant EF, $M_e(t) = t/t_{warm}$ for $0\leq t<t_{warm}$, and
$M_e(t) = 1$ for $t\geq t_{warm}$.
$j$ is the dissipative flux that is defined by
\begin{align}
  j = - \sum_{i=1}^N E_\infty q_i v_{i,x},
\end{align}
where $q_i$ is the partial charge of the $i$th atom, and $v_{i,x}$ is
the $x$ component of the velocity of the $i$th atom.  The notation
$\langle\cdot\rangle_0$ denotes the equilibrium ensemble average.
Eq.~\eqref{eqn:tmp1} can be found in the text books of statistical
mechanics (e.g.~M.~Tuckerman \emph{Statistical Mechanics: Theory and
  Molecular Simulation}, pp.~499).  We plot the correlation function
$\langle j(0)\cdot \chi_{_C}(t) \rangle_0$ against corrlation time $t$
in Fig.~\ref{fig:tmp1} of this reply. The value of the function is estimated from
two independent equilibrium simulation, and the trajactory of each is
of 1~$\mu$s. Please note that the total length of the equilibrium
trajactories is the same as the non-equilibrium simulation (2000
trajactories, each 1000~ps long).
% With the knowledge of
% non-equilibrium simulation, the correlation function is expected to
% vanish at roughly 500~ps, however, it does not vanish even at
% 1000~ps. This is not surprising, because
We find that the statistical error is even larger than the value of
corrlation function.  Therefore, the
overwhelming statistical uncertainty does not allow us to use it 
in Eq.~\eqref{eqn:tmp1} to calculate the
non-equilibrium averages. 
% , and we actually do not know when the
% corrlation function vanish .
Since the total computational effort of
the equilibrium simulation is the same as the non-equilibrium
simulation, we conclude that non-equilibrium simulatoin is more
precise than the conventional equilibrium approach (linear response) at the same computational cost.
A similar
observation has already been reported by Ciccotti and Jacucci, PRL
1975.
\\
% Another limit of the linear response theory is that it can only be
% used to calculate the non-equilibrium properties when the
% non-equilibrium purturbation to the system is small, and it is also
% impossible to tell \emph{a priori} if the purturbation is small enough
% that the response theory is valid. This issue also does not exist in
% our non-equilibrium simulation method.

@@

The frequency investigated in our manuscript is from 5~GHz to 100~GHz,
the largest of which is still one order of magnitude smaller than the
terahertz spectroscopy. Therefore, we find our simulation results
cannot be directly compared with the terahertz experiments.\\

@@

This is indeed a very interesting point. Although the Fig.11 is
plotted for the non-equilibrium oscillatory EF case, the
confromational transition pathways are qulitatively comparable to the
previous works on the transition pathways studied in equilibrium.
Both the connectivity of conformations and the relatively strength of
the transitions are similar. A short comment has been added to the
manuscript.

>>>>

Another commenly used equilibrium method that is able to study the non-equilibrium
responses is the linear responses thoery (Green-Kubo relation).
We also use it to test the
conformational shift of alanine dipeptide under the electric field
(EF). The response function, take the time-dependent probability of
left-handed $\alpha$-helix (Conformation $C$ in the old manuscript. The notation has been changed to $\alpha_L$ in the updated manuscript.) for example, is defined as
\begin{align}\label{eqn:tmp1}
  P_C(t) = \langle\chi_{_C}(t)\rangle = \langle \chi_{_C} \rangle_0 -
  \beta \int_0^t ds\; M_e(t - s)\langle j(0)\cdot \chi_{_C}(t) \rangle_0
\end{align}
where $\chi_{_C}$ is the characteristic function of set $C$ that takes
the value of 1 for $(\phi,\psi)\in C$, and takes value 0
otherwise. $M_e(t)$ is the magnitude of the EF. In the case of
constant EF, $M_e(t) = t/t_{warm}$ for $0\leq t<t_{warm}$, and
$M_e(t) = 1$ for $t\geq t_{warm}$.
$j$ is the dissipative flux that is defined by
\begin{align}
  j = - \sum_{i=1}^N E_\infty q_i v_{i,x},
\end{align}
where $q_i$ is the partial charge of the $i$th atom, and $v_{i,x}$ is
the $x$ component of the velocity of the $i$th atom.  The notation
$\langle\cdot\rangle_0$ denotes the equilibrium ensemble average.
Eq.~\eqref{eqn:tmp1} can be found in the text books of statistical
mechanics (e.g.~M.~Tuckerman \emph{Statistical Mechanics: Theory and
  Molecular Simulation}, pp.~499).  We plot the correlation function
$\langle j(0)\cdot \chi_{_C}(t) \rangle_0$ against corrlation time $t$
in Fig.~\ref{fig:tmp1} of this reply. The value of the function is estimated from
two independent equilibrium simulations, and the trajactory of each is
of 1~$\mu$s. Please note that the total length of the equilibrium
trajactories is the same as the non-equilibrium simulation (2000
trajactories, each 1000~ps long).
% With the knowledge of
% non-equilibrium simulation, the correlation function is expected to
% vanish at roughly 500~ps, however, it does not vanish even at
% 1000~ps. This is not surprising, because
We find that the statistical error is even larger than the value of
corrlation function.  Therefore, the
overwhelming statistical uncertainty does not allow us to use it 
in Eq.~\eqref{eqn:tmp1} to calculate the
non-equilibrium averages. 
% , and we actually do not know when the
% corrlation function vanish .
Since the total computational effort of
the equilibrium simulation is the same as the non-equilibrium
simulation, we conclude that non-equilibrium simulatoin is more
precise than the conventional equilibrium approach (linear response) at the same computational cost.
A similar
observation has already been reported by Ciccotti and Jacucci, PRL
1975. We have added the comparison between our non-equilibrium
simulation and the linear response thoery to an appendix of the manuscript.
\\
% Another limit of the linear response theory is that it can only be
% used to calculate the non-equilibrium properties when the
% non-equilibrium purturbation to the system is small, and it is also
% impossible to tell \emph{a priori} if the purturbation is small enough
% that the response theory is valid. This issue also does not exist in
% our non-equilibrium simulation method.

@@

The frequency investigated in our manuscript is from 5~GHz to 100~GHz,
the largest of which is still one order of magnitude smaller than the
terahertz spectroscopy. Therefore, we find our simulation results
cannot be directly compared with the terahertz experiments.
\recheck{please say something here}.
\\

@@

This is indeed a very interesting point.
Although the network presented Fig.11 is similar to those
discovered in the mentioned equilibrium studies,
in the sense of the steady conformations and connections among them,
the physical meaning is quit different in our study:
The system is under the nonequilibrium condition, and
the fluxes are directional and lasting (although the averged population of the steady conformations do not change). In contrast,
such probability fluxes do not exist in the equilibrium case.
A short comment has been added to the
manuscript.
